Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-02-17 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added section on event selection

%We will consider the events GW150915~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
%
%They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).

>>>>

%We will consider the events GW150915~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
%
%They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).
The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an \emph{IMR} model which infers the properties of the underlying GW signal, including independently its ringdown properties, using the Bayesian formalism above. Naturally, the most promising candidates for our analyses are high-mass \emph{and} loud GW observations with a significant signal-to-noise ratio (SNR) in the post-merger signal. The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed signals not all of which are relevant for a BH ringdown analysis. In fact, in an accompanying paper~\cite{LIGOScientific:2021sio}, the \textit{pSEOBNRv4HM} analysis~\footnote{Sec.VIII A.2 in ~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model presented in this paper, identified two events which provided the strongest bounds on measurements of the dominant $(220)$ QNM -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}. These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are extremely similar in their source properties. These are also two of the loudest BBH signals observed to date with a total network SNR of XX and XX respectively. Moreover, and what is most relevant for our analysis, is that their SNRs in the just the post-inspiral (merger-ringdown) part of the signal are the loudest to date, XX and XX respectively (corresponding tables in TGR GWTC-1/3) making them significantly promising as probes of the BH ringdown.
